Power simulation section

### 2023-09-07 docs/manuscript.Rmd
integrated shared first authorship info using papaja

author: 
  - name          : "Timo K. Koch*"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    #address       : "Postal address"
    email         : "timo.koch@unisg.ch"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Formal Analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Florian Pargent*"
    affiliation   : "1"
    role:
      - "Formal Analysis"
      - "Methodology"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Anne-Kathrin Kleine"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
  - name          : "Eva Lermer"
    affiliation   : "1,3"
    role:
      - "Resources"
  - name          : "Susanne Gaube"
    affiliation   : "1,4"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

@@

authornote: |
  \* The authors have contributed equally and share first authorship of this work.

>>>>

author: 
  - name          : "Timo K. Koch"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    #address       : "Postal address"
    email         : "timo.koch@unisg.ch"
    equal_contrib: yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Formal Analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Florian Pargent"
    affiliation   : "1"
    equal_contrib: yes
    role:
      - "Formal Analysis"
      - "Methodology"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Anne-Kathrin Kleine"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
  - name          : "Eva Lermer"
    affiliation   : "1,3"
    role:
      - "Resources"
  - name          : "Susanne Gaube"
    affiliation   : "1,4"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

@@

#authornote: |
  # author note here
